### 2017-07-14 eugene_notes.tex
moments

@@

% The second moment is
% \begin{align*}
%     \mL \ip{\phi}{X} \ip{\psi}{X}
%     &=
%     \frac{1}{N} \int \int \int \int
%     \left( \phi \left( \frac{y+z}{2} + \xi \right)
%          - \phi(x) \right)
%     \ip{\psi}{X}
%     (1 + \mu(x)) X(dx) X(dy) X(dz) e^{-(\xi/\eta)^2/2} d\xi \\
%     &\qquad {} +
%     \frac{1}{N} \int \int \int \int
%     \ip{\phi}{X}
%     \left( \psi \left( \frac{y+z}{2} + \xi \right)
%          - \psi(x) \right)
%     (1 + \mu(x)) X(dx) X(dy) X(dz) e^{-(\xi/\eta)^2/2} d\xi 
%     \\ &\qquad {} +
%     O(1/N^2)  \\
%     &=
%     \ip{\phi}{\partial_{\nu(X)} X} \ip{\psi}{X}
%     +
%     \ip{\phi}{X} \ip{\psi}{\nu(X)} 
%     + O(1/N^2)  \\
% \end{align*}

@@

If $Z$ is a fixed point of this flow,
then $\nu(Z)\ip{1+\mu}{Z} = (1+\mu)Z$.
We assume that $\mu(x) = 0$ on a nice smooth ``optimal'' manifold,
and that it increases with distance to the manifold.
With $\eta = 0$,
any fixed point is either a point mass,
or possibly uniform on the optimal manifold if it is linear.
We think an argument for this is obtained SOMETHING LIKE THE FOLLOWING: 
if $Z$ is a fixed point
and $\phi$ is a test function that is convex and increasing with distance from the optimal manifold,
then $\ip{\phi}{\nu(Z)} < \ip{\phi}{Z} < \ip{\phi}{(1+\mu)Z}/\ip{1+\mu}{Z}$,
since averaging contracts $Z$ while reweighting by $1+\mu$ expands $Z$.

@@

@@

\paragraph{Rough calculations of variances}
We did some of these,
by solving for $\sigma^2$ that was stable under
average $\to$ mollify $\to$ reweight by $1+\mu$,
assuming that fourth moments are $C$ times second moments, squared.

>>>>

\include{macros}

@@

@@

\paragraph{Stable measures}
If $Z$ is a fixed point of this flow,
then $\nu(Z)\ip{1+\mu}{Z} = (1+\mu)Z$.
We assume that $\mu(x) = 0$ on a nice smooth ``optimal'' manifold,
and that it increases with distance to the manifold.
With $\eta = 0$,
any fixed point is either a point mass,
or possibly uniform on the optimal manifold if it is linear.
We think an argument for this is obtained SOMETHING LIKE THE FOLLOWING: 
if $Z$ is a fixed point
and $\phi$ is a test function that is convex and increasing with distance from the optimal manifold,
then $\ip{\phi}{\nu(Z)} < \ip{\phi}{Z} < \ip{\phi}{(1+\mu)Z}/\ip{1+\mu}{Z}$,
since averaging contracts $Z$ while reweighting by $1+\mu$ expands $Z$.

@@

Any measure $Z$ that is a fixed point has the property that
(the average of two independent draws plus segregation noise)
is equal in distribution to
(a $1+\mu$-weighted draw).
Concretely, with $A$, $B$, and $C$ independent draws from $Z$,
$$\begin{aligned}
    \E\left[ f\left( \frac{A+B}{2} + \xi \right) \right]
    &=
    \frac{\E\left[ f(C) (1+\mu(C)) \right]}{\E[1+\mu(C)]} .
\end{aligned}$$
Let
$$\begin{aligned}
    m_k = \E[A^k] = \ip{x^k}{X} ,
\end{aligned}$$
and note that since $\E[\xi^w] = \eta^w (w-1)!!$ for even $w$,
$$\begin{aligned}
    \ip{x^k}{\nu(X)}
    &=
    \sum_{u+v+w=k} \binom{k}{u,v,w} 2^{w-k} m_u m_v \eta^w (w-1)!!.
\end{aligned}$$

We can calculate some things about this measure
for the case that $\mu(x) = ax^2$ 
(or generally, if this is a Taylor expansion).
Then
$$\begin{aligned}
    \frac{\E\left[ C^k (1+\mu(C)) \right]}{\E[1+\mu(C)]} 
    &=
    \frac{ m_k + a m_{k+2} }{ 1 + a m_2 } .
\end{aligned}$$
This gives us an equation for $m_{k+2}$ in terms of lower-order terms.
With $k=2$ and assuming that $Z$ is symmetric,
$$\begin{aligned}
    \frac{m_2}{2} + \eta^2
    &=
    \frac{ m_2 + a m_4 }{ 1 + a m_2 },
\end{aligned}$$
and so 
$$\begin{aligned}
    m_4
    &= m_2 \left( \eta^2 + \frac{1}{2} m_2 \right) 
       + \frac{1}{a} \left( \eta^2 - \frac{1}{2} m_2 \right) .
\end{aligned}$$
We believe that as $a \to 0$ this does not blow up,
implying that $m_2 = 2 \eta^2 + O(a)$,
and that in fact approaches Gaussian, for which $m_4 = 3m_2^2$,
and so $\eta^2 - m_2/2 = a \eta^2 + O(a^2)$,
and hence
$$\begin{aligned}
    m_2 &= 2 \eta^2 ( 1 - a \eta^2 ) + O(a^2)  \\
    m_4 &= 4 \eta^4 + O(a) .
\end{aligned}$$

If we take $1+\mu(x) = e^{ax^2}$,
then there is a Gaussian solution,
as is common in quant gen.
(Write this down in arbitrary dimensions!)

\paragraph{Fitness and load}
Note that since reproduction is unweighted,
fitness is proportional to lifetime,
so the fitness function is $1/(1+\mu(x)$.
Since replacement occurs at rate $\ip{1+\mu}{X}$,
the mean number of offspring per individual of type $x$
in population $X$ is $\ip{1+\mu}{X} / (1+\mu(x))$.

Take $\mu(x) = ax^2$.
The mean fitness in the population is then
$$\begin{aligned}
    \ip{1/(1+\mu)}{X}
    &=
    \ip{1 - ax^2 + a^2 x^4}{X} + O(a^3) \\
    &=
    1 - a m_2 + a^2 m_4 + O(a^3) \\
    &=
    1 - 2 a \eta^2 + 6 a^2 \eta^4 + O(a^3) ,
\end{aligned}$$
and the mean fitness of \emph{offspring} is
$$\begin{aligned}
    \ip{1/(1+\mu)}{\nu(X)}
    &=
    \ip{1 - ax^2 + a^2 x^4}{\nu(X)} + O(a^3) \\
    &=
    1 - a \left( \frac{m_2}{2} + \eta^2 \right) 
        + a^2 \left( 2 m_4 + 6 m_2^2 + 12 m_2 \eta^2 + 3 \eta^4\right) + O(a^3) \\
    &=
    1 - a \left( 2 \eta^2 - a \eta^4 \right)
        + a^2 \left( 8 \eta^4 + 24 \eta^4 + 24 \eta^4 + 3 \eta^4\right) + O(a^3) \\
    &=
    1 - 2 a \eta^2 + 60 a^2 \eta^4 + O(a^3) .
\end{aligned}$$
This implies that the difference in mean fitness between parents and offspring
(maybe this is called recombination load?)
is $54 a^2 \eta^4 + O(a^3)$.
(SOMETHING IS WRONG here because mean fitness in offspring should be less than in parents).

@@
